\chapter{Planning}
\label{ch:Planning}
\rrod{Create graphical planning}
\rrod{Create workday overview}
\rrod{Create week overview}
\rrow{Define deadlines}
\rrow{Define meetings: frequency, type, and already planned}

This chapter details the planning for the 40ECTS final thesis, carried out under the Robotics and Mechatronics Chair of the University of Twente. The Gantt planning for phase 1 and 2 can be found in appendix \ref{app:ganttplan} in figures \ref{fig:plan_phase1} and \ref{fig:plan_phase2} respectively.
\section{Workdays}
The planning is based on 28 hours per European Credit as per Dutch standard. The final thesis is carried out full-time (40 hours per week). The overview of working hours is shown in table \ref{tab:workdays}.
\begin{table} [h!]
	\begin{tabular}{l|ccc}
		\textbf{Day} 	&	Start time 		&	End time	&	Productive hours \\
		\hline
		\textbf{Monday} 		&	08:30	&	16:00	& 7 \\
		\rowcolor{Gray}
		\textbf{Tuesday} 	&	08:30 	&	17:00	& 8 \\
		\textbf{Wednesday} 	&	08:30	&	16:00	& 7 \\
		\rowcolor{Gray}
		\textbf{Thursday}	&	08:30	&	17:00	& 8 \\
		\textbf{Friday}		&	08:30	&	17:00	& 8 \\
		\rowcolor{Gray}
		\textbf{Miscellaneous}* & 		& 			& 2 \\
		\hline
		\textbf{Total:} 	&			&			& 40\\
	\end{tabular} \\
	\textit{* Miscellaneous hours are in evenings, weekends or during train rides.}
	\caption{Workdays and -hours}
	\label{tab:workdays}
\end{table}

\section{Work weeks}
\rroi{Discuss work days between christmas and new-year}
\rroi{Discuss work days on holidays}
The works weeks can be found in table \ref{tab:workweeks} in appendix \ref{app:workweeks}.

The project planning spans 35 weeks. Activities are planned from week 49 of 2018 up until, and including, week 28 of 2019 which spans a total of 32 weeks. Week 29 will be used to finalise practical aspects; handing in material and documentation, report printing, and so forth. The graduation presentation (and ceremony) will additionally take place in week 29. Weeks 30 and 31 of 2019 can serve as an extension if, and only if, approved by the assessment- and exam committee.

The planning takes into account one week around Christmas and new-years, one week spring break ("voorjaarsvakantie") in 2019, and a two week buffer. See section \ref{sec:off-days} for more details.
\newpage
\section{off-days} \label{sec:off-days}
The University of Twente recognises three general holidays, New Year's day, King's Birthday and Liberation day, and six Christian holidays, Good Friday, Easter Monday, Ascension day, Whit Monday, Christmas day, and Boxing day\footnote{\label{fn:web_holi} https://www.utwente.nl/en/ces/planning-schedules/academic-calendar/holidays-closing-days/}. Furthermore, the university recognises five bridging days in 2018 and fout bridging days in 2019 \footnote{\label{fn:col_clos} \raggedright https://www.utwente.nl/en/hr/terms-of-employment/scope-of-employment/public-holidays-leave-days/\#compulsory-leave-days}. 

Both the King's Birthday as well as Liberation day falls in weekends. The remainder of the holidays and bridging days are summarised in table \ref{tab:offdays}.

\begin{table} [h!]
	\begin{tabular}{l|lcl}
		\textbf{Holiday} 		&	Date 				&	Note \\
		\hline
		\textbf{Bridging day} 	& 	2018 December 24	& \textit{Collective closure\textsuperscript{\ref{fn:col_clos}}} \\
		\rowcolor{Gray}
		\textbf{Christmas day} 	&	2018 December 25	& \textit{Christian holiday\textsuperscript{\ref{fn:web_holi}}} \\ 
		\textbf{Boxing day} 	&	2018 December 26 	& \textit{Christian holiday\textsuperscript{\ref{fn:web_holi}}} \\
		\rowcolor{Gray}
		\textbf{Bridging day} 	&	2018 December 27	& \textit{Collective closure\textsuperscript{\ref{fn:col_clos}}} \\
		\textbf{Bridging day}	&	2018 December 28	& \textit{Collective closure\textsuperscript{\ref{fn:col_clos}}} \\
		\rowcolor{Gray}
		\textbf{Bridging day}	&	2018 December 31	& \textit{Collective closure\textsuperscript{\ref{fn:col_clos}}} \\
		\textbf{New Year's day} & 	2019 January 1	 	& General holidays\textsuperscript{\ref{fn:web_holi}} \\
		\rowcolor{Gray}
		\textbf{Good Friday}	&	2019 April 19	 	& \textit{Christian holiday\textsuperscript{\ref{fn:web_holi}}} \\
		\textbf{Easter Monday}	&	2019 April 22		& \textit{Christian holiday\textsuperscript{\ref{fn:web_holi}}} \\
		\rowcolor{Gray}
		\textbf{Ascension Day}	&	2019 May 30			& \textit{Christian holiday\textsuperscript{\ref{fn:web_holi}}} \\
		\textbf{Bridging day}	&	2019 May 31			& \textit{Collective closure\textsuperscript{\ref{fn:col_clos}}} \\
		\rowcolor{Gray}
		\textbf{Whit Monday}	&	2019 June 10		& \textit{Christian holiday\textsuperscript{\ref{fn:web_holi}}} \\
		\hline
	\end{tabular}
	\caption{Off-days}
	\label{tab:offdays}
\end{table}

Week 4 of 2019 is a planned vacation and no work will be done. This off-week spans from Monday 21\textsuperscript{st} of January 2019 until, and including, Friday 25\textsuperscript{th} of January 2019.


\rrot{Update time of lectures}
Currently, three lectures are planned which will result in an absent from the workplace in order to follow these lectures. These lectures are summarised in table \ref{tab:lectures}.

\begin{table} [h!]
	\begin{tabular}{l|lll}
		\textbf{Day} 		&	Date 		&	What	&	When \\
		\hline
		\textbf{Thursday}	&	2018 December 20	&	CT lecture	& Afternoon* \\
		\rowcolor{Gray}
		\textbf{Thursday} 	&	2019 January 10 	&	PET lecture	& Second half of afternoon* \\
		\textbf{Monday} 	&	2019 January 14		&	PET/SPECT Radiology	& Unknown* \\
		\hline
	\end{tabular} \\
	\textit{* Times will be updated when known}
	\caption{Planned lectures}
	\label{tab:lectures}
\end{table}